Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-04 submission/NatCom_appendix.tex
updated appendix
uodated figs

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Table & Figure & Jupyter Notebook \\
\hline
& \ref{fig:vgg-metrics}                                 & WeightWatcher-VGG.ipynb \\
& \ref{fig:resnet-accuracy}                             & WeightWatcher-ResNet.ipynb \\
& \ref{fig:resnet1k-accuracy}                           & WeightWatcher-ResNet-1K.ipynb \\
& \ref{fig:vgg-alpha-layers}                            & WeightWatcher-VGG.ipynb \\
& \ref{fig:resnet-alpha-layer}                          & WeightWatcher-ResNet.ipynb \\
& \ref{fig:densenet-alpha-layer}                        & WeightWatcher-DenseNet.ipynb \\
\hline
& \ref{fig:resnet204D5L}                                & WeightWatcher-Intel-Distiller-ResNet20.ipynb \\
\hline
& \ref{fig:GPT-hist}                                    & WeightWatcher-OpenAI-GPT.ipynb \\
& \ref{fig:gpt-alpha-layers}, \ref{fig:gpt2-histograms} & WeightWatcher-OpenAI-GPT2.ipynb \\
\hline
3,7,8,9 & Appendix & OSMR-Analysis.ipynb \\
\hline
\end{tabular}
\end{center}
\caption{Jupyter notebooks used to reproduce all results in Sections~\ref{sxn:cv} and~\ref{sxn:nlp}.\charles{Need to update referendes}}
\label{table:notebooks}
\end{table}

@@

We remove the following outliers, as identified by visual inspection: \texttt{efficient\_b0,\_b2}.
We also remove the entire \texttt{cifar100} \texttt{ResNeXT} series, which is the only example to show no trends with the norm metrics.
%
The final datasets used are shown in Table~\ref{table:datasets}.
The final architecture series used are shown in  Table~\ref{table:architectures}, with the number of models in each.

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Dataset & $\#$ of Models \\
\hline
imagenet-1k   &  76 \\
svhn          &  30 \\
cifar-100     &  26 \\
cifar-10      &  18 \\
cub-200-2011  &  12 \\
\hline
\end{tabular}
\end{center}
\caption{Datasets used \charles{This table needs updated}}
\label{table:datasets}
\end{table}

\input{table_6.tex}

%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ImageNet 1K]{
%%        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
%%        \label{fig:imagenet1k-alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 10 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
%%        \label{fig:cifar10.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 100 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
%%        \label{fig:cifar100.alpha}
%%    }
%%    \qquad
%%    \subfigure[ SVHN ]{
%%        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
%%        \label{fig:svhn.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CUB 200 ]{
%%        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
%%        \label{fig:cub200.alpha}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different datasets (as segmented in Table~\ref{table:datasets}).
%%            }
%%    \label{fig:DSalphas}
%%\end{figure}
%%
%% 
%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ ResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_01}
%%    }
%%    \subfigure[ SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_02}
%%    }
%%    \subfigure[ DIA-ResNet/DIA-PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_03}
%%    }
%%    \subfigure[ ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_04}
%%    }
%%    \subfigure[ WRN ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_05}
%%    }
%%    \subfigure[ DLA ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_06}
%%    }
%%    \subfigure[ PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_07}
%%    }
%%    \subfigure[ ProxylessNAS ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_08}
%%    }
%%    \subfigure[ VGG/BN-VGG ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_09}
%%    }
%%    \subfigure[ IGCV3 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_10}
%%    }
%%    \subfigure[ EfficientNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_11}
%%    }
%%    \subfigure[ SqueezeNext/SqNxt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_12}
%%    }
%%    \subfigure[ ShuffleNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_13}
%%    }
%%    \subfigure[ DRN-C/DRN-D ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_14}
%%    }
%%    \subfigure[ ESPNetv2 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_15}
%%    }
%%    \subfigure[ HRNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_16}
%%    }
%%    \subfigure[ SqueezeNet/SqueezeResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_17}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different architecture series (as segmented in Table~\ref{table:architectures}).
%%            }
%%    \label{fig:ARCHalphas}
%%\end{figure}
\input{table_RMSE.tex}
\input{table_R2.tex}
\input{table_Ktau.tex}

@@

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 (and Top5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the $R^{2}$ and $MSE$ for each metric, averaged over all regressions for all architectures and datasets.
\michael{Mention KTau.}
See Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The final analysis includes 108 regressions in all, those with 4 or more models, with a positive $R^2$.

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Table & Figure & Jupyter Notebook \\
\hline
1 & \ref{fig:vgg-metrics}                                 & WeightWatcher-VGG.ipynb \\
1 & \ref{fig:resnet-accuracy}                             & WeightWatcher-ResNet.ipynb \\
1 & \ref{fig:resnet1k-accuracy}                           & WeightWatcher-ResNet-1K.ipynb \\
1 & \ref{fig:vgg-alpha-layers}                            & WeightWatcher-VGG.ipynb \\
1 & \ref{fig:resnet-alpha-layer}                          & WeightWatcher-ResNet.ipynb \\
1 & \ref{fig:densenet-alpha-layer}                        & WeightWatcher-DenseNet.ipynb \\
\hline
& \ref{fig:resnet204D5L}                                & WeightWatcher-Intel-Distiller-ResNet20.ipynb \\
\hline
2 & \ref{fig:GPT-hist}                                    & WeightWatcher-OpenAI-GPT.ipynb \\
2 & \ref{fig:gpt-alpha-layers}, \ref{fig:gpt2-histograms} & WeightWatcher-OpenAI-GPT2.ipynb \\
\hline
3,7,8,9 & Appendix & OSMR-Analysis.ipynb \\
\hline
\end{tabular}
\end{center}
\caption{Jupyter notebooks used to reproduce all results in Sections~\ref{sxn:cv} and~\ref{sxn:nlp}.\charles{Need to update referendes}}
\label{table:notebooks}
\end{table}

@@

We remove the following outliers, as identified by visual inspection: \texttt{efficient\_b0,\_b2}.
We also remove the entire \texttt{cifar100} \texttt{ResNeXT} series, which is the only example to show no trends with the norm metrics.
%
%The final datasets used are shown in Table~\ref{table:datasets}.
The final architecture series used are shown in  Table~\ref{table:architectures}, with the number of models in each.

@@

%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ImageNet 1K]{
%%        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
%%        \label{fig:imagenet1k-alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 10 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
%%        \label{fig:cifar10.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 100 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
%%        \label{fig:cifar100.alpha}
%%    }
%%    \qquad
%%    \subfigure[ SVHN ]{
%%        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
%%        \label{fig:svhn.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CUB 200 ]{
%%        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
%%        \label{fig:cub200.alpha}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different datasets (as segmented in Table~\ref{table:datasets}).
%%            }
%%    \label{fig:DSalphas}
%%\end{figure}
%%
%% 
%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ ResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_01}
%%    }
%%    \subfigure[ SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_02}
%%    }
%%    \subfigure[ DIA-ResNet/DIA-PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_03}
%%    }
%%    \subfigure[ ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_04}
%%    }
%%    \subfigure[ WRN ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_05}
%%    }
%%    \subfigure[ DLA ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_06}
%%    }
%%    \subfigure[ PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_07}
%%    }
%%    \subfigure[ ProxylessNAS ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_08}
%%    }
%%    \subfigure[ VGG/BN-VGG ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_09}
%%    }
%%    \subfigure[ IGCV3 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_10}
%%    }
%%    \subfigure[ EfficientNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_11}
%%    }
%%    \subfigure[ SqueezeNext/SqNxt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_12}
%%    }
%%    \subfigure[ ShuffleNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_13}
%%    }
%%    \subfigure[ DRN-C/DRN-D ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_14}
%%    }
%%    \subfigure[ ESPNetv2 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_15}
%%    }
%%    \subfigure[ HRNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_16}
%%    }
%%    \subfigure[ SqueezeNet/SqueezeResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_17}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different architecture series (as segmented in Table~\ref{table:architectures}).
%%            }
%%    \label{fig:ARCHalphas}
%%\end{figure}
\input{table_RMSE}
\input{table_R2}
\input{table_Ktau}

@@

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 (and Top5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the $R^{2}$ and $MSE$ for each metric, averaged over all regressions for all architectures and datasets.
\michael{Mention KTau.}
See Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}.
In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The final analysis includes 108 regressions in all, those with 4 or more models, with a positive $R^2$.
